User-level Grid Monitoring with Inca 2

### 2007-02-28 papers/hpdc-gmw-2007/paper.tex
Update.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6598 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

The Inca agent is a server that implements the configuration specified by the
Inca administrator.  When it receives a configuration file from the Inca
administrator, it will determine which reporters should be executed on each
resource by expanding the resource macros and groups; it then stores the
expanded configuration information in the depot.  The agent stages and
launches an Inca component, called a reporter manager (described in the
following subsection), on each resource using either SSH or Globus.  Once a
reporter manager contacts its agent, the agent transmits the reporters to
execute along with their dependencies and a suite that contains their series
configuration and schedule of execution.  As an Inca administrator makes
updates to the configuration, the agent will push out new reporters and/or
suite changes to each of the affected resources.

To further manage the Inca deployment, the agent regularly pings the reporter
managers on each resource in order to detect when a reporter manager has
failed so it can be restarted.  For example, if a resource goes down for a
planned maintenance, the agent will attempt to restart the reporter manager
(by default every hour) until it succeeds.  The agent also maintains a local
cache of reporters and their dependencies; it periodically checks the
repositories for updates (every 4 hours by default) and automatically
distributes them to the reporter managers if the latest version is desired.  
The agent is implemented using Java.

@@

The Inca reporter manager is a lightweight process responsible for managing
the schedule and execution of Inca reporters on a single resource. The
reporter manager receives reporter updates and dependencies from the agent
along with requests for reporter scheduling changes.  Running under a regular
user account, the reporter manager executes reporters on-demand or using an
internal cron scheduler, and sends reports to the depot for archiving. The
reporter manager monitors reporter system usage using the system command
\texttt{ps} and enforces limits (e.g., wall clock time, CPU time, memory).
System usage information is sent to the depot with each report.

The reporter manager is implemented using Perl because Perl is available by default
on UNIX machines.  The cron scheduling is implemented using the CPAN Perl
module Schedule::Cron.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate} enabling the use of a variety of database backends.  The depot provides full archiving of reporter output and structures its schema
around series and the minimization of redundant data, i.e., only stores
changes from one report to another in a report series.  The depot also
supports comparisons that are executed on a newly received report; 
% need Jim's help with this sentence
currently regular expression matching and greater than/less than comparisons are 
supported.  Optionally, an Inca administrator can select to receive
email notification when the result of the comparison changes.

>>>>

The Inca agent is a server that implements the configuration specified by the
Inca administrator.  When the agent receives a configuration from incat,
it expands any resource group and macro references to determine
the series to execute on each resource and stores this
information in the depot.  The agent stages and
launches an Inca component, called a reporter manager (described in the
following subsection), on each resource, using either SSH or Globus.  After a
reporter manager contacts its agent, the agent transmits the reporters to
execute, any dependencies, and a suite that contains series
configuration and an execution schedule.  As an Inca administrator makes
updates to the configuration, the agent will push out new reporters and/or
suite changes to each of the affected resources.

The agent regularly pings its reporter managers in order to detect when one has
failed (for example, when a system is taken down for maintenance) and so must
be restarted.  The agent also maintains a local cache of reporters and their
dependencies; it periodically checks repositories (every 4 hours by default)
and automatically distributes reporter updates to the reporter managers as
needed.  The agent is implemented using Java.

@@

The Inca reporter manager is a lightweight process responsible for managing
the schedule and execution of Inca reporters on a single resource. The
reporter manager receives reporter updates and dependencies from the agent
along with requests for reporter scheduling changes.  Running under a regular
user account, the reporter manager executes reporters on-demand or using an
internal cron scheduler and sends reports to the depot for archiving. The
reporter manager monitors reporter system usage 
and enforces limits (e.g., wall clock time, CPU time, memory).
System usage information is sent to the depot with each report. 
The reporter manager is implemented using Perl to make it easy to install on
a wide variety of UNIX systems.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
The depot provides full archiving of reporter output, and the DB schema is
tuned to minimize redundant data.  Inca administrators can specify comparison
tests to run on reports as they are received, and the depot will send email
when the results of these comparisons change.  This provides the administrator
with quick notification of problems as they appear and of the results of
repairs.
